Centralized Programming for Distributed Control Planes

### 2016-01-26 paper/evaluation.tex
a new section to comment on the types of configs we generate
Add comparison for propane generated configs.

>>>>

\subsection{Propane-generated configurations}

Finally, we comment briefly on how the configurations generated by \sysname differ from those generated by operators today. In some cases, \sysname-generated configurations are implemented as one would expect. For example, preferences among neighboring ASes are implemented with a compiler-generated community value to tag incoming routes according to preference, which is then observed at other border routers to influence decisions. In other cases, the \sysname configurations are different, often relying on a different BGP mechanism to achieve the same result. For example, in one instance operators would use the no-export community to prevent routes from leaking beyond a certain tier of the data center, whereas \sysname would selectively import the route only below a certain tier. \sysname could use a similar implementation mechanism in the future as an optimization. In another instance, operators made assumptions about a neighboring AS to cut down on the propogation of route advertisements.
